Possibilistic evaluation of fuzzy temporal intervals

### 2011-11-28 estylf2012/estylf2012_en.tex
update for the estylf

The most convenient representation for the membership function of a fuzzy number is a triangular function. The membership function $\mu_M$ for the fuzzy set $M$ has also the properties of convexity and normalization. Three values represent a triangular function (see Figure~\ref{fig:triangular}):
\begin{itemize}
\item
$D$ is the singleton value in the core of $\mu_M(x)$.
\item
$D-a$ is the lower value in the support of $\mu_M(x)$. 
\item
$D+b$ is the upper value in the support of $\mu_M(x)$.
\end{itemize}
Note that the values $a$ and $b$ are values in the underlying ordered domain. E.g. $(a,b) \in \mathbb{R}^2$. The notation for a triangular function adopted here is $[D,a,b]$.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/triangular.pdf}
  \caption{Triangular function.}
  \label{fig:triangular}
\end{figure}

The most simple representation for the membership function of a fuzzy interval is a trapezoidal function. This membership function $\mu_T$ for the fuzzy interval $T$ is convex and normalized. Four values represent a trapezoidal membership function (figure  \ref{fig:trapezoidal}): $\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$. The membership function is given by:

\begin{align}
\mu_T(x)
\begin{cases}
1 & \mbox{ if } x \in [\beta,\gamma] \\
0 & \mbox{ if } x > \delta \vee x < \alpha \\
\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
\end{cases}
\end{align}

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/trapezoidalDistribution.pdf}
  \caption{Trapezoidal distribution.}
  \label{fig:trapezoidal}
\end{figure}

@@

% In such databases, points in time can be ill-known, i.e. the starting, the ending or both points are ill-known. a point in time is modelled as an ill-known value. When two such ill-known points are given, an interesting problem is the inference of uncertainty about the interval that is enclosed by these two ill-known points. In the proposed framework, this problem can be solved by evaluating an interval against two ill-known constraints, where the binary relations are ordering relations on the set of real numbers.

@@

\paragraph{Example} Consider the ill-known values $X = \left[5, 2, 8\right]$ and $Y = \left[9, 7, 10 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$  is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure~\ref{fig:3d-possibility} shows a 3D plot of the possibility that an interval $[a,b]$ passes the evaluations specified by the ill-known constraints. Note the triangular form for the resulting possibility distribution since the condition $a \leq b$ holds.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_possibility.pdf}
\caption{Possibility of evaluation for the interval $[a,b]$.}
\label{fig:3d-possibility}
\end{figure}
The necessity plot is obtained in a similar way and is shown in Figure~\ref{fig:3d-necessity}. Notice that the necessity measure is not normalized because the supports of $X$ and $Y$ overlap.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_necessity.pdf}
\caption{Necessity of evaluation for the interval $[a,b]$.}
\label{fig:3d-necessity}
\end{figure}

@@

\subsection{\label{subsubsec:transf-pres-imp}Transformation that preserves the imprecision}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.2]{graphs/preservingImprecision.pdf}
  \caption{Transformation of two fuzzy numbers into one fuzzy interval preserving the amount of imprecision.}
  \label{fig:transf-pres-imp}
\end{figure}
This transformation has been proposed in \cite{Garrido2009}. They assume that the imprecision of a fuzzy set is its area. Therefore the transformation consists of preserving the area of both fuzzy numbers that compose the interval. The transformation is performed by means of geometrical computations. The starting point of the fuzzy temporal interval is given by the fuzzy number $S = [d_s,a_s,b_s]$ respectively, the ending point of the fuzzy interval is given by $E = [d_e,a_e,b_e]$ (see Figure \ref{fig:transf-pres-imp}).

@@

The membership function for this fuzzy interval T is represented by the trapezoid $\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$:

\begin{align}
\nonumber
\alpha & =  d_s - a_s \\
\nonumber
\beta & = d_s + b_s \\
\nonumber
\gamma &= d_e - a_e \\
\nonumber
\delta &= d_e + b_e 
\end{align}

@@

%\paragraph{Comparison}
%In this subsection we will study the knowledge we have about the interval $[u,v]$ w.r.t. the fuzzy interval $T$  which is built preserving the imprecision as explained in Section \ref{subsubsec:transf-pres-imp}. Note that this approach is only valid when the supports of the original fuzzy numbers $X$ and $Y$ are disjoint (see Example \ref{ex:preserving-imprecision} below). Now, the knowledge we have about a number $u$ w.r.t. the transformated fuzzy interval $T$ is:
%\begin{eqnarray}
%\Pos\left(u\in T\right) &=& \mu_{T}\left(u\right) \\
%\Nec\left(u\in T\right) &=& 1 - \mu_{T}\left(u\right).
%\end{eqnarray}
%Therefore, the knowledge about an interval $[u,v]$ w.r.t. $T$ is:
%\begin{eqnarray}
%\nonumber
%\Pos\left([u,v]=T\right) &= \min \left(\Pos\left(u\in T\right),\Pos\left(v\in T\right)\right) &= \min \left(\mu_{T}\left(u\right),\mu_{T}\left(v\right)\right) \\
%\nonumber
%\Nec\left([u,v]=T\right) &= \min \left(\Nec\left(u\in T\right),\Nec\left(v\in T\right)\right) &= \min \left(1 - \mu_{T}\left(\overline{u},1 - \mu_{T}\left(\overline{v}\right)\right)\right)
%\end{eqnarray}

%\begin{example}
%\label{ex:preserving-imprecision}
\paragraph{Example}
In this example we are going to transform the two ill-known points $X= \left[5, 3, 3 \right]$ and $Y= \left[9, 2, 1 \right]$ into one fuzzy interval $T$ using the preserving the imprecision approach. Again, the two fuzzy numbers are represented by means of two triangular possibility distributions:

Then, following the equation presented in \eqref{eq:preserving-imprecision} we obtain the following trapezoidal shape:
\begin{equation}
\mu_{T}\left(x\right) = [d_s-a_s,d_s+b_s,d_e-a_e,d_e+b_e] = [2,8,7,10]
\end{equation}
This construction make no sense when the supports of the fuzzy numbers are disjoint. It is easy to build a rational membership function just by ordering the elements in the representation (e.g. $[2,7,8,10]$) but then, the amount of imprecision is not preserved at all. 
%\end{example}

\subsection{\label{subsubsec:trans-convex-hull}Transformation based on the convex hull}
The transformation based on the convex hull is more intuitive than the previous one. The transformation builds a trapezoidal possibility distribution with the left slope equal to the left slope of the starting fuzzy number (in the graphic, from $d_s-a_s$ to $d_s$) , the core equal to the interval $[d_s,d_e]$ and the right slope equal to the right slope of the ending fuzzy number (from $d_e$ to $d_e+b_e$). The interpretation of this convex hull is the ``most possible'' starting point and the ``most possible'' ending point. Figure \ref{fig:convexHull} shows the resulting transformation.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/convexHull.pdf}
  \caption{Transformation of two fuzzy numbers into one fuzzy interval with the convex hull approach.}
  \label{fig:convexHull}
\end{figure}

In this approach, the trapezoidal membership function ($\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$) is built in a different way:

\begin{align}
\nonumber
\alpha & =  d_s - a_s \\
\nonumber
\beta & = d_s \\
\nonumber
\gamma &= d_e  \\
\nonumber
\delta &= d_e + b_e 
\end{align}
%\paragraph{Comparison}
%Now, we will compare the knowledge we have about the interval $[u,v]$ w.r.t. the fuzzy interval $T$, which is the result of the convex hull transformation between the two fuzzy numbers $X$ and $Y$. The membership degree for the convex hull is given by:

%\begin{align}
%\label{eq:ch-possibility}
%\Pos\left([u,v]=T\right) &= \Pos\left(p^{\left(1\right)}\right) \cap \Pos\left(p^{\left(4\right)}\right) \\ 
%&= \min \left( \sup_{w \leq d}\ \mu_X\left(w\right) , \sup_{w \geq d}\ \mu_Y\left(w\right)\right)
%\end{align}

%The necessity measure for the convex hull is not consistent with the necessity measure for the individual fuzzy numbers $X$ and $Y$. This transformation results in an information lost.

%The necessity measures for the following predicates:

%\begin{align}
%\Nec\left(p^{\left(1\right)}\right) &=  \inf_{w \geq d} 1 - \mu_T\left(w\right) \\
%\Nec\left(p^{\left(4\right)}\right) &=  \inf_{w \leq d} 1 - \mu_T\left(w\right)
%\end{align}

%Therefore the necessity for the interval $[u,v]$ to be inside the fuzzy interval $T$ is:

%\begin{align}
%\label{eq:ch-necessity}
%\Nec\left([u,v]=T\right) &= \min \left(\Nec\left(p^{\left(1\right)}\right), p^{\left(4\right)}\right) \\
%& \min \left(\inf_{w \geq d} 1 - \mu_T\left(w\right),inf_{w \leq d} 1 - \mu_T\left(w\right)\right)
%\end{align}

%\begin{example}
\paragraph{Example}
In this example we are going to build the convex hull for the two ill-known starting and ending points $X= \left[5, 3, 3\right]$ and $Y = \left[9, 2, 1\right]$.

\begin{figure}[h!]
  \centering
 % \includegraphics[scale=0.2]{graphs/convexHull/convexHull.pdf}
 \input{scripts/convexhull.tex}
  \caption{Construction of the convex hull $T$ w.r.t the ill-known values $X$ and $Y$.}
  \label{fig:convex-hull-T}
\end{figure}

The convex hull for the fuzzy numbers $X$ and $Y$, represented by means of two triangular possibility distributions results in a trapezoidal possibility distribution with membership function $\mu_T(x)$ (see Figure \ref{fig:convex-hull-T}), represented by $[2,5,9,10]$.

%\begin{figure}[h!]
%  \centering
%  \includegraphics[scale=0.2]{graphs/convexHull/possAfterBefore.eps}
%  \caption{Possibility distributions for  both $u$ possibly greater or equal to $T$ and $u$ possibly smaller or equal to $T$.}
%  \label{fig:convex-hull-pos}
%\end{figure}

%\begin{align}
%\label{eq:ch-possibly-greater}
%\Pos\left(u \geq T\right) & = \sup_{d \leq u} \mu_{T}\left(d\right)  = [2,5,9,+\infty] \\
%\label{eq:ch-possibly-smaller}
%\Pos\left(u \leq T\right) & = \sup_{d \geq u} \mu_{T}\left(d\right)  = [-\infty,5,9,10] 
%\end{align}

%Respectively, the necessity mesaures for a point $u$ w.r.t. the convex hull $T$ are the following (Figure \ref{fig:convex-hull-nec}):

%\begin{align}
%\Nec\left(u \geq T\right) &=  1 - \Pos\left(u \geq T\right) = 1 - \sup_{d \geq u} \mu_{T}\left(d\right) = [9,10,+\infty,+\infty] \\ 
%\Nec\left(u \leq T\right) & = 1 - \Pos\left(u \geq T\right)  = \sup_{d \leq u} \mu_{T}\left(d\right)  = [-\infty,-\infty, 2,5]
%\end{align}

%\begin{figure}[h!]
%  \centering
%  \includegraphics[scale=0.2]{graphs/convexHull/necessity.eps}
%  \caption{Necessity distributions for both $u$ is necessarily greater or equal to $T$ and $u$ is necessarily smaller or equal to $T$.}
%  \label{fig:convex-hull-nec}
%\end{figure}

The membership about an interval $[u,v]$ w.r.t the convex hull $T$ is given by:

\begin{equation}
\label{eq:membership-ch}
\mu_T([u,v]) = \min \left( \mu_T\left(u\right), \mu_T\left(v\right)\right)
\end{equation}

Figure \ref{fig:ch-3d-possibility} shows the 3D plot of the membership function for any interval $[u,v]$ w.r.t. the convex hull $T$ (equation \eqref{eq:membership-ch}). Note that figure Figure \ref{fig:ch-3d-possibility} is equivalent to figure \ref{fig:3d-possibility}. Due to the transformation, it is impossible to obtain a necessity measure.

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{graphs/convexHull/3dpossibility.pdf}
  \caption{Membership function for interval $[u,v]$ w.r.t. the convex hull $T$.}
  \label{fig:ch-3d-possibility}
\end{figure}

%\begin{figure}[h!]
%  \centering
%  \includegraphics[scale=0.4]{graphs/convexHull/3dnecessity.eps}
%  \caption{Necessity of any interval $[u,v]$ w.r.t. the convex hull $T$.}
%  \label{fig:ch-3d-necessity}
%\end{figure}

%\end{example}

@@

%Submitted full papers are to be 4 to 6 pages length. Papers must be written on two columns with an overall width of 17.2 cm (8.25 cm each column and 0.7 cm of space between columns). On odd pages, left margin should be of 2.5 cm while the right one should be of 1.3 cm. On even pages, margins are just the contrary (left 1.3 cm, and right 2.5 cm). On all pages, odd and even ones, upper margin should be of 2.5 cm, and lower margin should be of 3.5 cm. Text alignment must be \textit{justify}. The pages must not be numbered.
%
%LaTeX style file (estylf\_en.sty) and the example file
%(estylf2012\_en.tex) are available in the ESTYLF2012 web page.
%
%\section{PRELIMINARIES}
%
%\subsection{SECTIONS AND SUBSECTIONS}
%
%\subsubsection{Subsection}
%All subsections must follow the same format as this one.
%
%\subsection{EQUATIONS}
%All equations must be centered.
%\begin{equation}
%\mu_A = f(a,b,c).
%\end{equation}
%
%\subsection{FIGURES}
%All figures must be centered like Figure~\ref{figure1}. The number and caption of the figure must always appear below the figure.

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=8cm,height=2.5cm]{estylf2012.jpg}
%\end{center}
%\caption{Example of figure caption.}
%\label{figure1}
%\end{figure}

%\subsection{TABLES}
%All tables must be centered and clear. The number and title always appear above the table (see Table~\ref{table1}).
%
%\begin{table}[ht]
%\begin{center}
%\caption{Example of table title.}
%\label{table1}
%\begin{tabular}{|c|l|} \hline
%\textbf{NAME} & \textbf{DESCRIPTION} \\ \hline
%$A$ & Fuzzy set \\ \hline
%$\mu_{A}$ & Membership function \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}

%\subsection{FOOTNOTES}
%Footnotes must be numbered\footnote{Example of footnote.}, and placed at the bottom of the column where they appear.
%
%\subsection{CITATIONS}
%Citations must include the reference number between square brackets, for example \cite{AlsinaT05}.

@@

%\begin{thebibliography}{99}

%\bibitem{AlsinaT05}
%C. Alsina, E. Trillas: On the symmetric difference of fuzzy sets. \emph{Fuzzy Sets and Systems} 153, pp.~181--194, 2005.
%
%\bibitem{Fishburn73}
%P.C. Fishburn: \emph{Utility Theory for Decision Making}. Wiley, New York, 1970.
%
%\bibitem{Yager03}
%R.R. Yager: E-Z OWA weights. In: \emph{Proceedings of the 10th IFSA World Congress}, Istanbul (Turkey), pp.~39--42, 2003.
%
%\bibitem{Zadeh71}
%L.A. Zadeh: Towards a theory of fuzzy systems. In: R.E. Kalman, N. DeClaris (Eds.), \emph{Aspects of Network and System Theory}, Holt, Rinehart and Winston, New York, pp.~469--490, 1971.

%\end{thebibliography}

%References must be sorted by the author name.

>>>>

The most convenient representation for the membership function of a fuzzy number is a triangular function. The membership function $\mu_M$ for the fuzzy set $M$ has also the properties of convexity and normalization. Three values represent a triangular function: %(see Figure~\ref{fig:triangular}):
\begin{itemize}
\item
$D$ is the singleton value in the core of $\mu_M(x)$.
\item
$D-a$ is the lower value in the support of $\mu_M(x)$. 
\item
$D+b$ is the upper value in the support of $\mu_M(x)$.
\end{itemize}
Note that the values $a$ and $b$ are values in the underlying ordered domain. E.g. $(a,b) \in \mathbb{R}^2$. The notation for a triangular function adopted here is $[D,a,b]$.
%\begin{figure}[h!]
%  \centering
%  \includegraphics[scale=0.4]{graphs/triangular.pdf}
%  \caption{Triangular function.}
%  \label{fig:triangular}
%\end{figure}

The most simple representation for the membership function of a fuzzy interval is a trapezoidal function. This membership function $\mu_T$ for the fuzzy interval $T$ is convex and normalized. Four values represent a trapezoidal membership function %(figure  \ref{fig:trapezoidal}):
 $\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$. The membership function is given by:

%\begin{align}
%\mu_T(x)
%\begin{cases}
%1 & \mbox{ if } x \in [\beta,\gamma] \\
%0 & \mbox{ if } x > \delta \vee x < \alpha \\
%\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
%\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
%\end{cases}
%\end{align}
%
%\begin{figure}[h!]
%  \centering
%  \includegraphics[scale=0.4]{graphs/trapezoidalDistribution.pdf}
%  \caption{Trapezoidal distribution.}
%  \label{fig:trapezoidal}
%\end{figure}

@@

@@

Note that the expressions in \eqref{eq:interval-pos},\eqref{eq:interval-nec} cannot be simplified in a more efficient expressions. %repensar
An ill-known point is given by a triangular membership function. The ill-known values $X$ and $Y$ are represented by the triangular membership functions $\left[D_X,a_X,b_X \right]$ and $\left[D_Y,a_Y,b_Y \right]$ respectively. The equation \eqref{eq:interval-pos} is derived to:

\begin{eqnarray}
\label{eq:interval-pos-triangular-a}
\sup_{a\geq w}\pi_{X}(w)=
\begin{cases}
0 & \mbox{\ if\ } a \leq \left( D_X - a_X \right) \\
1 & \mbox{\ if\ } a \geq D_X \\
 \frac{a-D_X+a_X}{a_X} & \mbox{\ if\ } a \in \left(D_X-a_X,D_X \right)
\end{cases}\\
\label{eq:interval-pos-triangular-b}
\sup_{b\leq w}\pi_{Y}(w)=
\begin{cases}
0 & \mbox{\ if\ } b \geq \left( D_Y + b_Y \right) \\
1 & \mbox{\ if\ } b \leq D_Y \\
 \frac{D_X+b_X-b}{b_X} & \mbox{\ if\ } b \in \left(D_Y,D_Y+b_Y \right) 
\end{cases}
\end{eqnarray}

The necessity expression of \eqref{eq:interval-nec} for triangular membership functions is given by:

\begin{eqnarray}
\label{eq:interval-nec-triangular-a}
\inf_{a<w}1-\pi_{X}(w)=
\begin{cases}
0 & \mbox{\ if\ } a \leq  D_X   \\
1 & \mbox{\ if\ } a \geq \left( D_X+b_X \right) \\
\frac{a}{b_X}- \frac{D_X}{b_X} & \mbox{\ if\ } a \in \left(D_X,D_X+b_X \right)
\end{cases}\\
\label{eq:interval-nec-triangular-b}
\inf_{b>w}1-\pi_{Y}(w)=
\begin{cases}
0 & \mbox{\ if\ } b \geq  D_Y \\
1 & \mbox{\ if\ } b \leq \left( D_Y - a_Y \right) \\
 \frac{D_Y-b}{a_X} & \mbox{\ if\ } b \in \left(D_Y,D_Y+b_Y \right) 
\end{cases}
\end{eqnarray}

\paragraph{Example} Consider the ill-known values $X = \left[3, 2, 1\right]$ and $Y = \left[7, 2, 3 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$ w.r.t. $X$ and $Y$ is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure \ref{fig:interval-rep} shows the graphical representation for the ill-known values $X$ and $Y$. The representation for equations \eqref{eq:interval-pos-triangular-a},\eqref{eq:interval-pos-triangular-b},\eqref{eq:interval-nec-triangular-a},\eqref{eq:interval-nec-triangular-b} are shown respectively in figures \ref{fig:interval_membership_pos_a},\ref{fig:interval_membership_pos_b},\ref{fig:interval_membership_nec_a},\ref{fig:interval_membership_nec_b}.

Consider now that the value for the interval $\left[a, b \right]$ is $\left[2, 6 \right]$. The evaluation for the possibility and necessity are:

\begin{eqnarray}
\label{eq:interval-pos}
\nonumber
\Pos\left(\lambda([3,6])\right)=\min(1,1)= 1\\
\label{eq:interval-nec}
\nonumber
\Nec\left(\lambda([3,6])\right)=\min(1,0.5 ) = 0.5
\end{eqnarray}

The main difference between this proposal and the transformations is that this framework always allows to obtain both possibility and necessity measures for each temporal comparison. In this case, there are the following possibilities:

\begin{itemize}
\item
$\Pos(\lambda([a,b])) = 0 \rightarrow \Nec(\lambda([a,b])) = 0$: The interval $[a,b]$ is not contained the fuzzy interval $[X,Y]$.
\item
$\Pos(\lambda([a,b])) > 0 $, $\Nec(\lambda([a,b])) = 0$: The interval $[a,b]$ is contained the fuzzy interval $[X,Y]$ but it is not inside the cores of both $X$ and $Y$.
\item
$\Pos(\lambda([a,b])) = 1 $, $\Nec(\lambda([a,b])) = 1$: The interval $[a,b]$ is contained the fuzzy interval $[X,Y]$ and it is inside the cores of both $X$ and $Y$.
\end{itemize}

\begin{figure}[h!]
\centering
\input{./graphs/interval.tex}
\caption{Triangular membership functions for the two ill-known time points $X$ and $Y$.}
\label{fig:interval-rep}
\end{figure}

\begin{figure}[h!]
\centering
\input{./graphs/interval_membership.tex}
\caption{Membership function for $\sup_{a\geq w}\pi_{X}(w)$.}
\label{fig:interval_membership_pos_a}
\end{figure}

\begin{figure}[h!]
\centering
\input{./graphs/interval_membership_b.tex}
\caption{Membership function for $\sup_{b\leq w}\pi_{Y}(w)$.}
\label{fig:interval_membership_pos_b}
\end{figure}

\begin{figure}[h!]
\centering
\input{./graphs/interval_membership_nec.tex}
\caption{Membership function for $\inf_{a<w}1-\pi_{X}(w)$.}
\label{fig:interval_membership_nec_a}
\end{figure}

\begin{figure}[h!]
\centering
\input{./graphs/interval_membership_nec_b.tex}
\caption{Membership function for $\inf_{b>w}1-\pi_{Y}(w)$.}
\label{fig:interval_membership_nec_b}
\end{figure}

@@

\subsection{\label{subsubsec:transf-pres-imp}Transformation that preserves the imprecision}
\begin{figure}[h!]
  \centering
  \input{./graphs/preserving_imp.tex}
  \caption{Transformation of two fuzzy numbers $X$ and $Y$ into one fuzzy interval $T$ preserving the amount of imprecision.}
  \label{fig:transf-pres-imp}
\end{figure}
This transformation has been proposed in \cite{Garrido2009}. They assume that the imprecision of a fuzzy set is its area. Therefore the transformation consists of preserving the area of both fuzzy numbers that compose the interval. The transformation is performed by means of geometrical computations. The starting point of the fuzzy temporal interval is given by the fuzzy number $S = [d_s,a_s,b_s]$ respectively, the ending point of the fuzzy interval is given by $E = [d_e,a_e,b_e]$ (see Figure \ref{fig:transf-pres-imp}).

@@

The membership function for this fuzzy interval T is represented by the trapezoid $\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$ and is equal to $\left[ d_s - a_s, d_s + b_s,d_e - a_e,d_e + b_e\right]$:

%\begin{align}
%\nonumber
%\alpha & =  d_s - a_s \\
%\nonumber
%\beta & = d_s + b_s \\
%\nonumber
%\gamma &= d_e - a_e \\
%\nonumber
%\delta &= d_e + b_e 
%\end{align}

@@

\paragraph{Example}
Consider the previous two ill-known points representing a time interval:  $X = \left[3, 2, 1\right]$ and $Y = \left[7, 2, 3 \right]$.
$P_1$ is the value for the transformation $T$, which is $\left[1,4,5,10 \right]$ (see figure \ref{fig:transf-pres-imp}. 
The value for $\left[a, b \right]$ is $\left[3,6 \right]$ therefore, the value for $P_2$ is $\left[3,3,6,6 \right]$. 
The knowledge about the interval $\left[a, b \right]$ w.r.t. the transformation $T$ using the preserving the imprecision approach is given by the \emph{CONTAINS} operator \cite{Garrido2009}.

\begin{eqnarray}
\nonumber
\mbox{CONTAINS}\left(P_1,P_2 \right) = \min \sup_{x} \left(1-\mu_{P_2}(x),\mu_{P_1}(x) \right) = \\
\nonumber
 \min (\mu_{\sup_x}(3),\mu_{\sup_x}(6) = \\
\nonumber
\min (\frac{2}{3},\frac{4}{5}) = \frac{2}{3} = 0.667
\end{eqnarray}

Figure \ref{fig:example_pi} shows the two membership degrees for both $\left(1-\mu_{P_2}(x)\right)$ and $\left( \mu_{P_1}(x) \right)$.

\begin{figure}[h!]
  \centering
  \input{./graphs/example_pi.tex}
  \caption{Graphical representation for the membership functions $\left(1-\mu_{P_2}(x)\right)$ and $\left( \mu_{P_1}(x) \right) $.}
  \label{fig:example_pi}
\end{figure}

In this example it is shown how this transformation is misleading: it is clear that the temporal interval $[3,6]$ is completely contained by the fuzzy temporal interval represented by $[X,Y]$. Nevertheless, the \emph{CONTAINS} operator applied to this transformation returns a 0.667 membership degree. Therefore, if the user is looking for a temporal interval $[a,b]$ and the database contains a tuple with a fuzzy interval $[X,Y]$, this transformation returns a possibility below 1, thus the user may interprete that the temporal interval $[a,b]$ is not completely inside the fuzzy interval $[X,Y]$. Plus, there is not possible to compute a necessity measure for the \emph{CONTAINS} operator in order to obtain more information about $[a,b]$.

\subsection{\label{subsubsec:trans-convex-hull}Transformation based on the convex hull}
The transformation based on the convex hull is more intuitive than the previous one. The transformation builds a trapezoidal possibility distribution with the left slope equal to the left slope of the starting fuzzy number (in the graphic, from $d_s-a_s$ to $d_s$) , the core equal to the interval $[d_s,d_e]$ and the right slope equal to the right slope of the ending fuzzy number (from $d_e$ to $d_e+b_e$). The interpretation of this convex hull is the ``most possible'' starting point and the ``most possible'' ending point. Figure \ref{fig:convex-hull-T} shows the resulting transformation.

In this approach, the trapezoidal membership function ($\left[\alpha,\ \beta,\ \gamma,\ \delta\right]$) is built in a different way: $\left[d_s - a_s,d_s,d_e,d_e + b_e \right]$

%\begin{align}
%\nonumber
%\alpha & =  d_s - a_s \\
%\nonumber
%\beta & = d_s \\
%\nonumber
%\gamma &= d_e  \\
%\nonumber
%\delta &= d_e + b_e 
%\end{align}

\paragraph{Example}
Consider again the previous two ill-known points representing a time interval:  $X = \left[3, 2, 1\right]$ and $Y = \left[7, 2, 3 \right]$.
$P_1$ is the value for the transformation $T$, which is $\left[1,3,7,10 \right]$ 
The value for $\left[a, b \right]$ is $\left[3,6 \right]$ therefore, the value for $P_2$ is $\left[3,3,6,6 \right]$. 
The evaluation for the \emph{CONTAINS} operator is the following:

\begin{eqnarray}
\nonumber
\mbox{CONTAINS}\left(P_1,P_2 \right) = \min \sup_{x} \left(1-\mu_{P_2}(x),\mu_{P_1}(x) \right) = \\
\nonumber
\min \sup_{x} \left(1,1 \right) = 1
\end{eqnarray}

Figure \ref{fig:example_ch} shows the two membership degrees for both $\left(1-\mu_{P_2}(x)\right)$ and $\left( \mu_{P_1}(x) \right)$.

\begin{figure}[h!]
  \centering
  \input{./graphs/example_ch.tex}
  \caption{Graphical representation for the membership functions $\left(1-\mu_{P_2}(x)\right)$ and $\left( \mu_{P_1}(x) \right) $.}
  \label{fig:example_ch}
\end{figure}

This transformation is also misleading. Even though the possibility obtained is similar to the possibility obtained in our proposal, there is not possible to compute the necessity for the \emph{CONTAINS} operator. Therefore, it is not possible to obtain a complete information for the interval $[a,b]$ w.r.t the fuzzy interval $[X,Y]$.

\begin{figure}[h!]
  \centering
 \input{./graphs/convexhull.tex}
  \caption{Construction of the convex hull $T$ w.r.t the ill-known values $X$ and $Y$.}
  \label{fig:convex-hull-T}
\end{figure}

@@

@@
